Fast Algorithms for Intersection of Non-matching Grids Using \plucker Coordinates.

### 2016-11-30 paper_intersections.tex
Another improvement of plucker signs explanation.

%\newcommand{\noteJB}[1]{{\color{Blue} \textbf{JB: } \textit{#1}}}
%\newcommand{\notePE}[1]{{\color{Orange} \textbf{PE: } \textit{#1}}}
\newcommand{\noteJB}[1]{}
\newcommand{\notePE}[1]{}

@@

The sign of the permuted inner product tells us the relative position of two lines, 
which is demonstrated on an example of a relative position of a line and a triangle sides in \fig{fig:plucker_products}.

\begin{figure}[!htb]
    \centering
    \subfloat[$\pi_p\odot \pi_{s_i} < 0 \;\forall i$]{
        \includegraphics[width=0.3\textwidth]{\figpath plucker_product_a.pdf}
    }
    \subfloat[$\pi_p\odot \pi_{s_i} = 0 \, \exists i$ \newline special]{
        \includegraphics[width=0.3\textwidth]{\figpath plucker_product_b.pdf}
    }
    \subfloat[$\pi_p\odot \pi_{s_i} > 0 \;\forall i$]{
        \includegraphics[width=0.3\textwidth]{\figpath plucker_product_c.pdf}
    }
    \caption{Different relative positions of a line $p$ and a triangle with sides $s_i$, $i=0,1,2$. 
            Signs of the permuted inner products depend on orientation of lines.          
            Dashed line symbolizes that the line is in the back, the lines intersect in the middle case.
            We see that in cases a and c the products have the same sign.
    }
    \label{fig:plucker_products}
\end{figure}

@@

The calculation of the intersection proceeds as follows:
\begin{enumerate}
    \item Compute or reuse \plucker coordinates and permuted inner products: $\pi_p$, $\pi_{s_i}$, $\pi_p \odot \pi_{s_i}$, for $i=1,2,3$.
    \item Compute barycentric coordinates $w_i,\ i=1,2,3$ using \eqref{eq:bary_centric}.
    \item If any $w_i$ is less than $\epsilon$, there is no intersection, return empty IP.  
    \item If all $w_i$ are greater than $\epsilon$, we set $\tau_{S_2} = (2, 0)$ for the IC.
    \item If one $w_i$ is less than $\epsilon$, intersection is on the edge $s_i$, we set $\tau_{S_2} =(1,i)$.
    \item If two $w_i$ are less than $\epsilon$, intersection is at the vertex $V_i$, we set $\tau_{S_2}=(0,i)$.
    \item \label{item:coplanar} If all $w_i$ are less than $\epsilon$, the line is coplanar with the triangle, both objects are 
        projected to the plane $x_i=0$ where $i$ is the index of the maximal component of the triangle's normal vector.
        Every pair $p$, $s_i$ is checked for an intersection on $S_2$ boundary either inside $s_i$ or at a vertex $V_i$, setting the topological info $\tau_{S_2}$ to 
        $(1, i)$ or $(0, i)$, respectively. At most two ICs are obtained.
    \item For each IC the barycentric coordinates $(1-t, t)$ on the line $p$ are computed according to \eqref{eq:line}. 
    \item If $t\in (-\epsilon, \epsilon)$ or $t\in (1-\epsilon, 1+\epsilon)$,
        we set the end point of $S_1$: $\tau_{S_1} = (0,0)$ or $\tau_{S_1} = (0,1)$, respectively.
    \item If $t\notin (-\epsilon, 1+\epsilon)$, the IC is eliminated.
\end{enumerate}

@@

-

>>>>

\newcommand{\noteJB}[1]{{\color{Blue} \textbf{JB: } \textit{#1}}}
\newcommand{\notePE}[1]{{\color{Orange} \textbf{PE: } \textit{#1}}}
% \newcommand{\noteJB}[1]{}
% \newcommand{\notePE}[1]{}

@@

The sign of the permuted inner product tells us the relative position of two lines. 
We shall demonstrate this on an example of a relative position of a line and triangle sides in \fig{fig:plucker_products}.
The permuted inner products have the same sign in cases a and c, which will be later used as an indicator
that an intersection inside the triangle exists.
If any $\pi_p\odot \pi_{s_i}$ is zero, as in case b, it means that the lines $p$ and $s_i$ are intersecting each other
(note that $s_i$ are considered as infinite lines at the moment).
Any other situation not depicted in \fig{fig:plucker_products} is charaterized by different signs of permuted inner products.

\begin{figure}[!htb]
    \centering
    \subfloat[$\pi_p\odot \pi_{s_i} < 0 \;\forall i$]{
        \includegraphics[width=0.3\textwidth]{\figpath plucker_product_a.pdf}
    }
    \subfloat[$\pi_p\odot \pi_{s_i} = 0 \, \exists i$ \newline special]{
        \includegraphics[width=0.3\textwidth]{\figpath plucker_product_b.pdf}
    }
    \subfloat[$\pi_p\odot \pi_{s_i} > 0 \;\forall i$]{
        \includegraphics[width=0.3\textwidth]{\figpath plucker_product_c.pdf}
    }
    \caption{Different relative positions of a line $p$ and a triangle with sides $s_i$, $i=0,1,2$. 
            Signs of the permuted inner products depend on orientation of lines.          
            Dashed line symbolizes that the line is in the back, the lines intersect in the middle case.
    }
    \label{fig:plucker_products}
\end{figure}

@@

The calculation of the intersection proceeds as follows:
\begin{enumerate}
    \item Compute or reuse \plucker coordinates and permuted inner products: $\pi_p$, $\pi_{s_i}$, $\pi_p \odot \pi_{s_i}$, for $i=1,2,3$.
    \item Compute barycentric coordinates $w_i,\ i=1,2,3$ using \eqref{eq:bary_centric}.
    \item If any $w_i$ is less than $-\epsilon$ \notePE{I believe there was minus missing.}, there is no intersection, return empty IP. 
          Compare \fig{fig:plucker_products} and \eqref{eq:bary_centric} for better insight.
    \item If all $w_i$ are greater than $\epsilon$, we set $\tau_{S_2} = (2, 0)$ for the IC.
    \item If one $w_i$ is less than $\epsilon$, intersection is on the edge $s_i$, we set $\tau_{S_2} =(1,i)$.
    \item If two $w_i$ are less than $\epsilon$, intersection is at the vertex $V_i$, we set $\tau_{S_2}=(0,i)$.
    \item \label{item:coplanar} If all $w_i$ are less than $\epsilon$, the line is coplanar with the triangle, both objects are 
        projected to the plane $x_i=0$ where $i$ is the index of the maximal component of the triangle's normal vector.
        Every pair $p$, $s_i$ is checked for an intersection on $S_2$ boundary either inside $s_i$ or at a vertex $V_i$, setting the topological info $\tau_{S_2}$ to 
        $(1, i)$ or $(0, i)$, respectively. At most two ICs are obtained.
    \item For each IC the barycentric coordinates $(1-t, t)$ on the line $p$ are computed according to \eqref{eq:line}. 
    \item If $t\in (-\epsilon, \epsilon)$ or $t\in (1-\epsilon, 1+\epsilon)$,
        we set the end point of $S_1$: $\tau_{S_1} = (0,0)$ or $\tau_{S_1} = (0,1)$, respectively.
    \item If $t\notin (-\epsilon, 1+\epsilon)$, the IC is eliminated.
\end{enumerate}

@@
